SunPy - Python for Solar Physics

### 2014-01-28 3-2-HEK.tex
added SDO FFT reference back in

The Sun is an active star and exhibits a wide range of transient phenomena (e.g. flares, 
radio burst) on many 
different time-scales, length-scales and wavelengths. Observations and metadata 
concerning these phenomena are collected at the Heliophysics Event 
Knowledgebase (HEK).  Entries are generated both by automated algorithms and 
human observers.  Some of the information in the HEK reproduces feature/event 
data elsewhere (for example, the GOES flare catalog), and some is generated by 
the Solar Dynamics Observatory Feature Finding Team \cite{SDOFFT paper???} to
populate the HEK.  The advantage of the HEK is it provides a homogeneous and 
well-described interface to a large 
amount of feature/event information of interest to the solar physics community.

>>>>

The Sun is an active star and exhibits a wide range of transient phenomena (e.g. flares, 
radio burst) on many 
different time-scales, length-scales and wavelengths. Observations and metadata 
concerning these phenomena are collected at the Heliophysics Event 
Knowledgebase (HEK).  Entries are generated both by automated algorithms and 
human observers.  Some of the information in the HEK reproduces feature/event 
data elsewhere (for example, the GOES flare catalog), and some is generated by 
the Solar Dynamics Observatory Feature Finding Team \cite{martens2012} to
populate the HEK.  The advantage of the HEK is it provides a homogeneous and 
well-described interface to a large 
amount of feature/event information of interest to the solar physics community.
